Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-03-06 Paper/paper.tex
Add Table 2

\begin{table*}
  % In published version of this table, we could remove file names and add data homogenisation in Notes.
  % Add z ~ 7 qso when you add it to analysis
  % See data.tex for a version of this table that includes file names
  \caption{Quasar data sets}
  \label{tab:samples}
  \begin{tabular}{crcllrSl}
    \hline
    & ID & $z$ & Survey & Reference & Number & {Area} & Notes \\
    & & & & & of quasars & {(deg$^2$)} & \\
    \hline
    1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \\
    2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \\
    3. & 15  & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \\
    4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \\
    5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & Restricted to $z<4.7$ \\
    6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & Overlaps with 8 for $M_{1450}<-26.73$ \\
    7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \\
    8. &  8 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \\
    9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \\
    10. & 8 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \\
    11. & 6 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \\
    12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \\
    13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & Rescaled selection probabilities \\
    14. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \\
    15. & 18 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \\
    16. & 18 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \\
    17. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \\
    18. & 10 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \\
    19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \\
    20. & 19 & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 & \\
    21. & 19 & 6.5--7.4 & UKIDSS & \citet{2007MNRAS.376L..76V} & 1 & 3370.0 & \\
  \end{tabular}
\end{table*}

@@

\subsection{Luminosity function estimates in redshift bins}

@@

>>>>

\begin{table*}
  % In published version of this table, we could remove file names and add data homogenisation in Notes.
  % Add z ~ 7 qso when you add it to analysis
  % See data.tex for a version of this table that includes file names
  \caption{Quasar data sets}
  \label{tab:samples}
  \begin{tabular}{crcllrSl}
    \hline
    & ID & $z$ & Survey & Reference & Number & {Area} & Notes \\
    & & & & & of quasars & {(deg$^2$)} & \\
    \hline
    1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \\
    2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \\
    3. & 15  & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \\
    4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \\
    5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & Restricted to $z<4.7$ \\
    6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & Overlaps with 8 for $M_{1450}<-26.73$ \\
    7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \\
    8. &  8 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \\
    9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \\
    10. & 8 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \\
    11. & 6 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \\
    12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \\
    13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & Rescaled selection probabilities \\
    14. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \\
    15. & 18 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \\
    16. & 18 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \\
    17. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \\
    18. & 10 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \\
    19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \\
    20. & 19 & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 & \\
    21. & 19 & 6.5--7.4 & UKIDSS & \citet{2007MNRAS.376L..76V} & 1 & 3370.0 & \\
    \hline
  \end{tabular}
\end{table*}

@@

\begin{table*}
  % bins_tabulate.py; Nqso added by hand
  \caption{Best-fit double power law luminosity function parameters in
    various redshift bins.  The luminosity function parameters
    $\phi_*$, $M_*$, $\alpha$, and $\beta$ are defined in
    Equation~(\ref{eqn:dpl}), with $\beta$ denoting the faint-end
    slope.  Quasars in each bin have redshifts $z_\mathrm{min}\leq z <
    z_\mathrm{max}$.  The number of quasars in each bin is given by
    $N_\mathrm{qso}$.  The bin centre and sample mean redshift are
    given by $z_\mathrm{bin}$ and $\langle z\rangle$, respectively.
    Errors indicate one-sigma (68.26\%) uncertainties.  These values
    are shown in Figure~\ref{fig:evoln}.  The corresponding luminosity
    functions are shown in Figure~\ref{fig:mosaic}.  See
    Section~\ref{sec:bins} for further details.}
  \label{tab:bins}
  \begin{tabular}{ccccrcccc}
    \hline
    $\langle z\rangle$ & $z_\mathrm{bin}$ & $z_\mathrm{min}$ & $z_\mathrm{max}$ & $N_\mathrm{qso}$ & $\log_{10}(\phi_*/$ & $M_*$ & $\alpha$ & $\beta$ \\
    & & & & & cMpc$^{-3}$mag$^{-1}$) & & & \\
    \hline
    $0.31$ & $0.25$ & $0.10$ & $0.40$ & 3520 & $-5.62^{+0.09}_{-0.10}$ & $-21.37^{+0.21}_{-0.22}$ & $-2.94^{+0.09}_{-0.10}$ & $-1.22^{+0.18}_{-0.16}$ \\
    $0.50$ & $0.50$ & $0.40$ & $0.60$ & 4555 & $-6.12^{+0.04}_{-0.04}$ & $-23.00^{+0.08}_{-0.08}$ & $-3.37^{+0.07}_{-0.08}$ & $-1.36^{+0.04}_{-0.04}$ \\
    $0.72$ & $0.70$ & $0.60$ & $0.80$ & 3308 & $-6.42^{+0.09}_{-0.08}$ & $-24.03^{+0.15}_{-0.13}$ & $-3.55^{+0.12}_{-0.13}$ & $-1.75^{+0.05}_{-0.04}$ \\
    $0.91$ & $0.90$ & $0.80$ & $1.00$ & 3922 & $-6.39^{+0.08}_{-0.07}$ & $-24.51^{+0.12}_{-0.11}$ & $-3.69^{+0.10}_{-0.11}$ & $-1.73^{+0.06}_{-0.05}$ \\
    $1.10$ & $1.10$ & $1.00$ & $1.20$ & 6367 & $-6.53^{+0.03}_{-0.03}$ & $-25.14^{+0.04}_{-0.04}$ & $-4.17^{+0.08}_{-0.09}$ & $-1.73^{+0.02}_{-0.02}$ \\
    $1.30$ & $1.30$ & $1.20$ & $1.40$ & 6479 & $-6.43^{+0.04}_{-0.04}$ & $-25.29^{+0.06}_{-0.06}$ & $-3.97^{+0.08}_{-0.08}$ & $-1.74^{+0.03}_{-0.03}$ \\
    $1.50$ & $1.50$ & $1.40$ & $1.60$ & 7539 & $-6.51^{+0.03}_{-0.03}$ & $-25.68^{+0.04}_{-0.04}$ & $-4.28^{+0.08}_{-0.08}$ & $-1.75^{+0.02}_{-0.02}$ \\
    $1.71$ & $1.70$ & $1.60$ & $1.80$ & 6788 & $-6.28^{+0.04}_{-0.04}$ & $-25.55^{+0.05}_{-0.05}$ & $-3.96^{+0.07}_{-0.07}$ & $-1.60^{+0.03}_{-0.03}$ \\
    $1.98$ & $2.00$ & $1.80$ & $2.20$ & 10478 & $-6.72^{+0.03}_{-0.03}$ & $-26.26^{+0.04}_{-0.04}$ & $-4.20^{+0.07}_{-0.07}$ & $-1.87^{+0.02}_{-0.02}$ \\
    $2.25$ & $2.25$ & $2.20$ & $2.30$ & 4102 & $-5.98^{+0.10}_{-0.09}$ & $-25.26^{+0.19}_{-0.18}$ & $-3.21^{+0.15}_{-0.16}$ & $-1.54^{+0.07}_{-0.06}$ \\
    $2.35$ & $2.35$ & $2.30$ & $2.40$ & 4317 & $-6.28^{+0.09}_{-0.09}$ & $-25.63^{+0.17}_{-0.15}$ & $-3.39^{+0.17}_{-0.19}$ & $-1.64^{+0.06}_{-0.05}$ \\
    $2.45$ & $2.45$ & $2.40$ & $2.50$ & 3403 & $-6.40^{+0.08}_{-0.07}$ & $-25.86^{+0.14}_{-0.13}$ & $-3.60^{+0.20}_{-0.21}$ & $-1.60^{+0.05}_{-0.05}$ \\
    $2.65$ & $2.65$ & $2.60$ & $2.70$ & 1883 & $-5.98^{+0.06}_{-0.06}$ & $-25.15^{+0.14}_{-0.13}$ & $-3.13^{+0.12}_{-0.13}$ & $-1.05^{+0.09}_{-0.08}$ \\
    $2.75$ & $2.75$ & $2.70$ & $2.80$ & 1135 & $-6.30^{+0.08}_{-0.07}$ & $-25.96^{+0.15}_{-0.13}$ & $-3.81^{+0.28}_{-0.31}$ & $-1.34^{+0.07}_{-0.06}$ \\
    $2.85$ & $2.85$ & $2.80$ & $2.90$ & 1069 & $-6.46^{+0.12}_{-0.10}$ & $-26.23^{+0.23}_{-0.18}$ & $-3.60^{+0.36}_{-0.42}$ & $-1.46^{+0.08}_{-0.07}$ \\
    $2.95$ & $2.95$ & $2.90$ & $3.00$ & 1104 & $-6.77^{+0.07}_{-0.06}$ & $-26.53^{+0.10}_{-0.09}$ & $-5.05^{+0.60}_{-0.64}$ & $-1.71^{+0.05}_{-0.04}$ \\
    $3.05$ & $3.05$ & $3.00$ & $3.10$ & 1127 & $-6.77^{+0.08}_{-0.07}$ & $-26.48^{+0.12}_{-0.10}$ & $-4.71^{+0.46}_{-0.52}$ & $-1.70^{+0.06}_{-0.05}$ \\
    $3.15$ & $3.15$ & $3.10$ & $3.20$ & 1041 & $-7.25^{+0.17}_{-0.12}$ & $-27.09^{+0.25}_{-0.18}$ & $-4.42^{+0.81}_{-1.23}$ & $-1.96^{+0.08}_{-0.06}$ \\
    $3.25$ & $3.25$ & $3.20$ & $3.30$ & 815 & $-7.33^{+0.13}_{-0.13}$ & $-27.19^{+0.19}_{-0.23}$ & $-4.36^{+0.65}_{-0.76}$ & $-1.93^{+0.06}_{-0.06}$ \\
    $3.34$ & $3.35$ & $3.30$ & $3.40$ & 510 & $-7.54^{+0.19}_{-0.21}$ & $-27.39^{+0.25}_{-0.37}$ & $-4.90^{+1.36}_{-1.35}$ & $-2.08^{+0.09}_{-0.07}$ \\
    $3.44$ & $3.45$ & $3.40$ & $3.50$ & 155 & $-6.77^{+0.19}_{-0.20}$ & $-26.64^{+0.42}_{-0.35}$ & $-3.70^{+0.62}_{-0.80}$ & $-1.24^{+0.27}_{-0.22}$ \\
    $3.88$ & $3.90$ & $3.70$ & $4.10$ & 628 & $-7.92^{+0.12}_{-0.10}$ & $-27.26^{+0.14}_{-0.12}$ & $-4.81^{+0.34}_{-0.39}$ & $-2.07^{+0.10}_{-0.09}$ \\
    $4.35$ & $4.40$ & $4.10$ & $4.70$ & 442 & $-8.32^{+0.29}_{-0.26}$ & $-27.38^{+0.38}_{-0.31}$ & $-4.19^{+0.41}_{-0.47}$ & $-2.20^{+0.16}_{-0.13}$ \\
    $4.92$ & $5.10$ & $4.70$ & $5.50$ & 263 & $-9.02^{+0.29}_{-0.22}$ & $-27.88^{+0.36}_{-0.27}$ & $-4.51^{+0.66}_{-0.83}$ & $-2.31^{+0.11}_{-0.08}$ \\
    $6.00$ & $6.00$ & $5.50$ & $6.50$ & 66 & $-10.60^{+0.71}_{-1.06}$ & $-29.12^{+1.04}_{-1.78}$ & $-4.99^{+0.72}_{-1.22}$ & $-2.40^{+0.10}_{-0.08}$ \\
    \hline
  \end{tabular}
\end{table*}

\subsection{Luminosity function estimates in redshift bins}
\label{sec:bins}

@@

%% Tables:
%% Individual fit results
%% Global models best fit parameters
%% Emissivity (H and He)
%% Photoionization rates (H and He)
%%
